---
title: "Methodology & Data Preparation"
site: distill::distill_website
toc: TRUE
toc_depth: 3
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set("_site/Methodology_files")

library(dplyr)
library(knitr)
library(tidyverse)
library(clock)
```

<h2> Methodology </h2>

<p>
With the objectives sorted out as well as, the way to solve each problem can be planned in advanced by visualizing the following graphs.
</p>

<p>
1.	Heatmap of businesses by each period, this would highlight popular places in a timeframe based on the number of transactions happening.
2.	A map of the region with points showing the start and end point of each trip would give meaning to the popularity of the places as well as could find new leads regarding the routines of each employee.
3.	The combination of the loyalty card data as well as the routine of the employees acquired from the vehicle data would give a possibility of which card belonging to which employee. However, multiple employees in the same place at the same time would make this impossible. 
4.	Network graph to show non-professional relationships between employees.
5.	A combination of the above visualizations would be enough to infer any suspicious activities done by the employees. Therefore, no additional visualizations would be needed.
</p>

<h2> Data Preparation </h2>

<p>
To start the investigation, the dataset must first be prepared to be able to be properly plotted which will be discussed in this sub-section.
</p>

<h3> Transaction Heatmap </h3>
<p>
To begin with, this part will utilize the "cc_data" and "loyalty_data" csv files. Some problems found and how it is solved are listed below.
</p>

1. Incorrect data formats
```{r,echo=TRUE}
cc <- read.csv("_site/Methodology_files/cc_data.csv")
loyalty <- read.csv("_site/Methodology_files/loyalty_data.csv")
print(str(cc))
print(str(loyalty))
```
<p>
As can be seen above, the first thing needed to be fixed is the timestamp columns of each dataframe since they are still reported as "character" instead of a "datetime" format. This is done by extracting the date using the "date_time_parse" function from the "clock" library.
</p>
```{r,echo=TRUE}
cc$timestamp <-  date_time_parse(cc$timestamp,zone = "", format = "%m/%d/%Y %H:%M")
loyalty$timestamp <-  date_time_parse(loyalty$timestamp,zone = "", format = "%m/%d/%Y")

print(str(cc))
print(str(loyalty))
```
2. Create new dataframes
<p>
The heatmap is planned to analyze a combination of credit cards, loyalty cards, number of transactions and revenue. As such different dataframes must be prepared in order to successfully visualize all aspects.
</p>
```{r,echo=TRUE}
## Extract hour row from cc data


cc$H <-  format(cc$timestamp, format='%H')

## Create only mdy column in cc for matching with loyalty

cc$mdy <- format(cc$timestamp, format = "%m/%d/%Y")
cc$mdy <- date_time_parse(cc$mdy,zone = "",format = "%m/%d/%Y")

## Extract transactions that use loyalty card but not CC using dplyr

loy_only <-  anti_join(loyalty,cc,by=c("location","price","timestamp"="mdy"))

## Extract transactions that use cc only

cc_only <- anti_join(cc,loyalty,by=c("location","price","mdy"="timestamp"))

## Create transactions that use both

cc_loy_union <- merge(cc,loyalty,by.x=c("location","price","mdy"),by.y=c("location","price","timestamp"),all=TRUE)

cc_loy_clean <-  na.omit(cc_loy_union)
row.names(cc_loy_clean) <- NULL
```

<p>
Once the dataframes has been created, the plotting follows the same code chunk shown below.
</p>
```{r,echo=TRUE}
library(viridis)
library(ggplot2)
library(hrbrthemes)
library(plotly)

x <- paste("H",seq(0,23),sep="")
y <- sort(unique(cc$location))
data <- expand.grid(X=x, Y=y)
data$H <- seq(0,23)

for(i in 1:nrow(data)){
  data$Z[i] =  nrow(cc_loy_clean[cc_loy_clean$location == data$Y[i] 
                                 & cc_loy_clean$H == data$H[i],])
}

data <- data %>%
  mutate(text = paste0("Hour: ", X, "\n","Location: ", Y, "\n","Number of Transactions: ", Z, "\n"))

p <- ggplot(data, aes(X, Y, fill= Z,text=text)) + 
  geom_tile() +
  scale_fill_viridis(discrete=FALSE) +
  theme_ipsum()

plot1 <- ggplotly(p, tooltip="text")
```
```{r,echo=FALSE,layout="1-body-outset",fig.height=7}
plot1
```

<h3> GPS Movements </h3>

<p>
Tracking the GPS movements is a more demanding task considering the sheer size of the dataset. However, as discussed in the methodology, only the start and endpoint will be considered for plotting. This section will discuss how to filter said data as well as how to plot the data on top of an overlay image of the map of Kronos.
</p>

<h4> Filter Only Start and End Points </h4>