---
title: "Credit Card and Loyalty Card Owners"
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
library(DT)
```

<p>
This page will list the credit card and loyalty card owners as well as the likelihood level of the employee owning that card. The level is defined as:

0 = Unable to find owner

1 = A chance to be the owner of this card

2 = Likely to own this card

3 = Very likely to own this card
</p>

<p>
A likelihood level of 1 would mean that the employee's location in a specific time matches the transaction time using a specific card. However, there is too many people in that interval as well as other timeframes that makes it hard to confidently determine that the card belongs to a specific employee. As the number of employees in a place reduces, the more easier it is to determine the card owner and as such the likelihood level will also increase.
</p>
<p>
As for the level 0, reasons may arise which makes it unable to pinpoint who owns the card for sure. An additional column is added to explain the reason.
</p>

```{r,echo=FALSE}
ownership <- read.csv("cardowners.csv")
datatable(ownership)
```




