---
title: "Credit Card and Loyalty Card Owners"
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
library(DT)
```

<p>
This page will list the credit card and loyalty card owners as well as the likelihood level of the employee owning that card. The level is defined as:
</p>
<p>
0 = Cannot give any confidence of identifying a specific employee as an owner of a card
</p>
<p>
1 = Positional data or time data may not be in-sync, could be person was in the vicinity or at the exact place but outside of the time window by a few minutes without anyone else being a possible answer. 
</p>
<p>
2 = Cross-check of transaction data and positional data shows person was the only possible person to use this card at that time

</p>
<p>
For a level 0, reasons may arise which makes it unable to pinpoint who owns the card for sure. An additional column is added to explain the reason.
</p>

```{r,echo=FALSE}
ownership <- read.csv("cardowners.csv")
datatable(ownership)
```
<p>
Important to note regarding conflicting loyalty card numbers. During data processing, the first instance of a purchase is what the loyalty card takes. However, during identification of owner, the date was randomly selected. Therefore, there is a chance that the conflicting owners would mean a possibility of a stolen credit card as the loyalty card belongs to the original owner then the other person uses it at a later date.
</p>




